\textbf{NAME OF THIS STUDY}

### 2018-11-07 submission/manuscript.Rmd
table for model parameters added

```{r knitr_settings, eval=TRUE, echo=FALSE, cache=FALSE,  warning=FALSE, message=FALSE}
# Load useful functions
source('../code/learning/functions.R')
# Read in necessary libraries
deps = c("doParallel","pROC", "caret","knitr","rmarkdown","vegan","gtools", "tidyverse");
for (dep in deps){
  if (dep %in% installed.packages()[,"Package"] == FALSE){
    install.packages(as.character(dep), quiet=TRUE);
  }
  library(dep, verbose=FALSE, character.only=TRUE)
}
opts_chunk$set("tidy" = TRUE)
opts_chunk$set("echo" = FALSE)
opts_chunk$set("eval" = TRUE)
opts_chunk$set("warning" = FALSE)
opts_chunk$set("cache" = FALSE)

@@

	if(is.numeric(x)){
		if(abs(x - round(x)) < .Machine$double.eps^0.5){
			paste(format(x,big.mark=',', digits=0, scientific=FALSE))
		} else {
			paste(format(x,big.mark=',', digits=1, nsmall=1, scientific=FALSE))
		}
	} else {
    	paste(x)      
	}
}
knitr::knit_hooks$set(inline=inline_hook)
```

@@

```{r model_parameters, echo=FALSE, results='asis'}
model_param <- read.table('../data/process/model_parameters.txt', header=T, sep='\t')
kable(model_param, caption = "Table 1 Parameters and software implementation of the classification algorithms")
```
\vspace{35mm}

@@

**Figure 1. Number of OTUs sampled among bacterial and archaeal 16S rRNA gene sequences for different OTU definitions and level of sequencing effort.** Rarefaction curves for different OTU definitions of Bacteria (A) and Archaea (B). Rarefaction curves for the coarse environments in Table 1 for Bacteria (C) and Archaea (D).

>>>>

```{r knitr_settings, eval=TRUE, echo=FALSE, cache=FALSE,  warning=FALSE, message=FALSE}
# Read in necessary libraries
deps = c("doParallel","pROC", "caret","knitr","rmarkdown","vegan","gtools", "tidyverse");
for (dep in deps){
  if (dep %in% installed.packages()[,"Package"] == FALSE){
    install.packages(as.character(dep), quiet=TRUE);
  }
  library(dep, verbose=FALSE, character.only=TRUE)
}
opts_chunk$set("tidy" = TRUE)
opts_chunk$set("echo" = FALSE)
opts_chunk$set("eval" = TRUE)
opts_chunk$set("warning" = FALSE)
opts_chunk$set("cache" = FALSE)

@@

	if(is.numeric(x)){
		if(abs(x - round(x)) < .Machine$double.eps^0.5){
			paste(format(x,big.mark=',', digits=0, scientific=FALSE))
		} else {
			paste(format(x,big.mark=',', digits=1, nsmall=1, scientific=FALSE))
		}
	} else {
    	paste(x)      
	}
}
knitr::knit_hooks$set(inline=inline_hook)
options(kableExtra.latex.load_packages = FALSE)
options(kableExtra.auto_format = FALSE)
options(knitr.table.format = "latex")
library(kableExtra)
```

@@

```{r model_parameters, echo=FALSE, results='asis'}
model_param <- read.table('../data/process/model_parameters.txt', header=T, sep='\t') %>% 
   select(Method, Parameter, Cross.Validation, Epochs, Scaler, Sklearn.Function) %>% 
  rename("Cross Validation"="Cross.Validation") %>%
  rename("Epoch"="Epochs") %>%
  rename("Sklearn Function"="Sklearn.Function")

Table1 <- kable(model_param, "latex", caption = "Optimized hyper-parameters, pre-processing and cross-validation methods and software implementation of the classification algorithms", booktabs = T) %>%
kable_styling(latex_options = c("striped", "scale_down"), position = "left") %>%  
 column_spec(1, width="10em") %>%
  column_spec(2, width="8em") %>% 
  column_spec(3, width="9em") %>%
  column_spec(5, width="5em") %>% 
  row_spec(1:7, align="l") %>% 
  row_spec(0,bold=TRUE)

param_range <- read.table('../data/process/model_parameters.txt', header=T, sep='\t', na.strings="", stringsAsFactors = FALSE) %>% 
  replace(is.na(.), "-") %>%  
  select(-Value, -Parameter, -Cross.Validation, -Epochs, -Scaler, -Sklearn.Function)

Table2 <- kable(param_range, "latex", caption = "The range of optimized hyper-parameters for each of the classification algorithms", booktabs = T) %>%
kable_styling(latex_options = c("striped", "scale_down"), position = "left")%>%
 column_spec(2:3, width="5em")

```
\vspace{35mm}

@@

**Figure 1. Generalization and classification performance of modeling methods ** AUC values of all cross validation and testing performances.
```{r}
```

```{r}
Table1
```
\newpage

### 2018-11-07 submission/manuscript.tex
table for model parameters added

@@

\begin{verbatim}
## pdf 
##   2
\end{verbatim}

@@

\textbf{Figure 1. Number of OTUs sampled among bacterial and archaeal
16S rRNA gene sequences for different OTU definitions and level of
sequencing effort.} Rarefaction curves for different OTU definitions of
Bacteria (A) and Archaea (B). Rarefaction curves for the coarse
environments in Table 1 for Bacteria (C) and Archaea (D).

>>>>

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}

@@

@@

\textbf{Figure 1. Generalization and classification performance of
modeling methods } AUC values of all cross validation and testing
performances.
\includegraphics{manuscript_files/figure-latex/unnamed-chunk-1-1.pdf}

\rowcolors{2}{gray!6}{white}

\begin{table}

\caption{\label{tab:model_parameters}Optimized hyper-parameters, pre-processing and cross-validation methods and software implementation of the classification algorithms}
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{8em}>{\raggedright\arraybackslash}p{9em}r>{\raggedright\arraybackslash}p{5em}l}
\hiderowcolors
\toprule
\textbf{Method} & \textbf{Parameter} & \textbf{Cross Validation} & \textbf{Epoch} & \textbf{Scaler} & \textbf{Sklearn Function}\\
\midrule
\showrowcolors
\multicolumn{1}{>{\raggedright\arraybackslash}p{10em}}{Logistic Regression} & \multicolumn{1}{>{\raggedright\arraybackslash}p{8em}}{C} & \multicolumn{1}{>{\raggedright\arraybackslash}p{9em}}{5-fold, 100-repeats} & \multicolumn{1}{l}{100} & \multicolumn{1}{>{\raggedright\arraybackslash}p{5em}}{MinMax} & \multicolumn{1}{l}{LogisticRegression}\\
\multicolumn{1}{>{\raggedright\arraybackslash}p{10em}}{L1 SVM Linear Kernel} & \multicolumn{1}{>{\raggedright\arraybackslash}p{8em}}{C} & \multicolumn{1}{>{\raggedright\arraybackslash}p{9em}}{5-fold, 100-repeats} & \multicolumn{1}{l}{100} & \multicolumn{1}{>{\raggedright\arraybackslash}p{5em}}{Standard} & \multicolumn{1}{l}{LinearSVC}\\
\multicolumn{1}{>{\raggedright\arraybackslash}p{10em}}{L2 SVM Linear Kernel} & \multicolumn{1}{>{\raggedright\arraybackslash}p{8em}}{C} & \multicolumn{1}{>{\raggedright\arraybackslash}p{9em}}{5-fold, 100-repeats} & \multicolumn{1}{l}{100} & \multicolumn{1}{>{\raggedright\arraybackslash}p{5em}}{Standard} & \multicolumn{1}{l}{LinearSVC}\\
\multicolumn{1}{>{\raggedright\arraybackslash}p{10em}}{SVM RBF Kernel} & \multicolumn{1}{>{\raggedright\arraybackslash}p{8em}}{C, gamma} & \multicolumn{1}{>{\raggedright\arraybackslash}p{9em}}{5-fold, 100-repeats} & \multicolumn{1}{l}{100} & \multicolumn{1}{>{\raggedright\arraybackslash}p{5em}}{Standard} & \multicolumn{1}{l}{SVC}\\
\multicolumn{1}{>{\raggedright\arraybackslash}p{10em}}{Decision Tree} & \multicolumn{1}{>{\raggedright\arraybackslash}p{8em}}{max\_depth, min\_samples\_split} & \multicolumn{1}{>{\raggedright\arraybackslash}p{9em}}{5-fold, 100-repeats} & \multicolumn{1}{l}{100} & \multicolumn{1}{>{\raggedright\arraybackslash}p{5em}}{MinMax} & \multicolumn{1}{l}{DecisionTreeClassifier}\\
\addlinespace
\multicolumn{1}{>{\raggedright\arraybackslash}p{10em}}{Random Forest} & \multicolumn{1}{>{\raggedright\arraybackslash}p{8em}}{n\_estimators, max\_features} & \multicolumn{1}{>{\raggedright\arraybackslash}p{9em}}{5-fold, 100-repeats} & \multicolumn{1}{l}{100} & \multicolumn{1}{>{\raggedright\arraybackslash}p{5em}}{MinMax} & \multicolumn{1}{l}{RandomForestClassifier}\\
\multicolumn{1}{>{\raggedright\arraybackslash}p{10em}}{XGBoost} & \multicolumn{1}{>{\raggedright\arraybackslash}p{8em}}{n\_estimators, colsample\_bytree, learning\_rate, subsample, max\_depth, min\_child\_weight} & \multicolumn{1}{>{\raggedright\arraybackslash}p{9em}}{5-fold, 100-repeats} & \multicolumn{1}{l}{100} & \multicolumn{1}{>{\raggedright\arraybackslash}p{5em}}{MinMax} & \multicolumn{1}{l}{XGBClassifier}\\
\bottomrule
\end{tabular}}
\end{table}

\rowcolors{2}{white}{white} \newpage
